DeepPicar:​ ​A​ ​Low-cost​ ​Deep​ ​Neural​ ​Network-based​ ​Autonomous​ ​Car

### 2017-10-07 paper/overview.tex
Edited overview

Another issue we observed in training/testing the network, which could
affect the network performance, is camera latency. In DeepPicar's
context, the camera latency is the time from the time the camera
sensor observes the scene to the time the computer actually read the
digitized image data. Unfortunately, this time can be substantially
long depending on the camera and the computer performance. We
experimentally measure DeepPicar's camera latency as
follows~\footnote{We follow the method and the tool found at
  https://www.makehardware.com/2016/03/29/finding-a-low-latency-webcam/}.
First, we point the DeepPicar's camera toward to a computer monitor, which is
conntected to the Raspberry Pi 3's HDMI output. We then launch a
simple program that overlay the current time with the camera's preview
screen on the monitor. Then, infinite number of time strings will be
shown on the monitor screen and the time difference between the two
successive time strings represent the camera
latency. Figure~\ref{fig:camera-latency} shows the captured moniotor
screen. The measured camera latency is about 300~350 ms. This is
significantly higher than a human's perception latency, which is known
to be as fast as 13 ms~\cite{ThomasBurger2015}. Higher camera latency
could negatively affect to the control performance as the DNN would
analyze stale scenes. In the future, we plan to identify and use
low-latency cameras.

>>>>

Another issue we observed in training/testing the network, which could
affect the network performance, is camera latency. In DeepPicar's
context, the camera latency is the time from the time the camera
sensor observes the scene to the time the computer actually reads the
digitized image data. Unfortunately, this time can be significantly
long depending on camera and the computer performance. We
experimentally measure DeepPicar's camera latency as
follows~\footnote{We follow the method and the tool found at
  https://www.makehardware.com/2016/03/29/finding-a-low-latency-webcam/}.
First, we point the DeepPicar's camera toward to a computer monitor, which is
conntected to the Raspberry Pi 3's HDMI output. We then launch a
simple program that overlays the current time with the camera's preview
screen on the monitor. Then, an infinite number of time strings will be
shown on the monitor screen and the time difference between the two
successive time strings represent the camera
latency. Figure~\ref{fig:camera-latency} shows the captured moniotor
screen. The measured camera latency is about 300~350 ms. This is
significantly higher than the latency of human perception, which is known
to be as fast as 13 ms~\cite{ThomasBurger2015}. Higher camera latency
could negatively affect to the control performance as the DNN would
analyze stale scenes. In the future, we plan to identify and use
low-latency cameras.
